NumPy---Array Computation for Python

### 2019-12-10 paper.tex
Start NEP section

>>>>

Following Python's practice of using Python Enhancement Proposals (PEPs) for
``proposing major new features, for collecting community input on an
issue, and for documenting the design decisions that have gone into Python,''
we began using NumPy Enhancement Proposals (NEPs) in 2007.
This process was informal and only occasionally used until 2017 when
we adopted a more formal process \footnote{\url{https://numpy.org/neps/nep-0000.html}}.
Since then there have been 19 proposed NEPS---6 have been implemented,
4 have been accepted and are being implemented, 4 are under consideration,
3 have deferred or superseded, and 2 have been rejected or withdrawn.
We highlight a few of the implemented NEPs below.
